\label{sec:Conclusions}
Preview control has been studied for at least four decades and a large number of theoretical results can be found in the control and mechanical engineering technical literature. In many cases the theoretical developments on discrete-time $\htwo$/LQG were driven by applications problems. Contemporary applications include for example active automotive suspension control \cite{Roh_1999_Stoc_Opt_Prev,Marzbanrad_2004_SuspPrev}, helicopter flight control \cite{Paulino_2006_PreviewRotorcraftAffine}, 
and driver steering control \cite{Cole_2006_PredictiveAndPreviewSteeringControl}.
Other applications examples, which are also related to vehicle dynamics problems, can be found in the first author's thesis; visit \url{http://code.google.com/p/preview-control-toolbox/}. A MATLAB Preview Control toolbox implementing the presented algorithms, together with their $\hinf$ counterpart, can also be obtained from this site.

In the authors' opinion the strong influence of applications problems has produced a body of theory that is example-specific and consequently somewhat restricted in terms of its scope and generality. To the best of our knowledge a complete set of tools for synthesising $\htwo$ preview controllers that solve a broad range of realistic design problems is unavailable in the open literature. The provision of these tools is the central purpose of the work presented here. We present a general preview problem that captures most of the results in the contemporary literature, as well as offering a solution framework for more complex preview problems such as the preview tracking with integral action problem illustrated in Figure \ref{fig:TrackSysIntegDesign}.

The preview control problem studied in this paper is shown in Figure~\ref{fig:DistRejSys}, and  comprises a plant that is controlled by a two-degree-of-freedom controller. The controller is synthesized to optimize the closed-loop system's response to a combination of previewable and non-previewable exogenous inputs.  The presented solution includes an efficient computational framework that is based on two low-order Riccati equations with dimension that of the plant (excluding the preview delay line). This algorithm also includes an efficient computation of the perfect information controller gains as well as the controller itself. We have also provided an efficient method for finding the $\htwo$ norm of the closed-loop system, and a method for evaluating the norm reduction due to preview as $N \rightarrow \infty$. As is shown in Figures~\ref{fig:PrevContStruct} and \ref{fig:PrevContStructxp}, the controller structure is essentially low order with the preview part implemented using an efficient finite-impulse-response section. 
